### 2022-07-23 paper/localpsf.tex
including the meshHeight plot which shows the axes and ultimately the scale of the domain U

\begin{figure}[H]
	\begin{subfigure}{0.6\textwidth}
		\includegraphics[scale=0.25]{meshHeight_view2_edges.png}
		\caption{Bird's eye view}
	\end{subfigure}
	\begin{subfigure}{0.38\textwidth}
		\includegraphics[scale=0.15]{meshHeight_view0_edges_withColorBar.png}
		\caption{Top-down view}
	\end{subfigure}
	\caption{The ice sheet, discretized by a mesh of tetrahedra. Color indicates the height of the base of the ice sheet (i.e., the mountain topography).}
	\label{fig:ice_mountain_mesh}
\end{figure}

@@

\begin{figure}[H]
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{True $m$.}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.18]{trueVelocity_glyphs_withColorBar.png}
		\caption{True $\bm{u}$.}
	\end{subfigure}
	\caption{True logarithmic basal sliding parameter $\basalfriction$ (left) and true velocity $\bm{u}$ (right). In the right plot, arrows indicate the direction of $\bm{u}$ and color indicates the magnitude of $\bm{u}$.}
\end{figure}

\begin{figure}[H]
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m1_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter1}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m3_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter2}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m4_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter3}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m6_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter4}
	\end{subfigure}
	%\begin{subfigure}{0.05\textwidth}
	%	\includegraphics[scale=0.1]{mColorBar.png}
	%\end{subfigure}
	\caption{The parameter after $1$ (left), $3$ (second from left), $4$ (third from left) Newton iterates and the final Newton iterate (right). The preconditioner is constructed between Newton iterations 3 and 4.} 
\end{figure}

>>>>

\begin{figure}[H]
	\begin{subfigure}{0.6\textwidth}
		\includegraphics[scale=0.25]{meshHeight_view2_edges.png}
		\caption{Bird's eye view}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[scale=0.15]{meshHeight_view0_edges_withAxes.png}
		\caption{Top-down view}
	\end{subfigure}
	\caption{The ice sheet, discretized by a mesh of tetrahedra. Color indicates the height of the base of the ice sheet (i.e., the mountain topography).}
	\label{fig:ice_mountain_mesh}
\end{figure}

@@

\begin{figure}[H]
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{True $\basalfriction$.}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.18]{trueVelocity_glyphs_withColorBar.png}
		\caption{True $\bm{u}$.}
	\end{subfigure}
	\caption{True logarithmic basal sliding parameter $\basalfriction$ (left) and true velocity $\bm{u}$ (right). In the right plot, arrows indicate the direction of $\bm{u}$ and color indicates the magnitude of $\bm{u}$.}
\end{figure}

\begin{figure}[H]
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m1_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter1}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m3_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter2}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m4_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter3}
	\end{subfigure}
	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m6_psf.png}
		%		\caption{}
		%		\label{fig:newtoniter4}
	\end{subfigure}
	%\begin{subfigure}{0.05\textwidth}
	%	\includegraphics[scale=0.1]{mColorBar.png}
	%\end{subfigure}
	\caption{The log basal friction parameter $\basalfriction$ after $1$ (left), $3$ (second from left), $4$ (third from left) Newton iterates and the final Newton iterate (right). The preconditioner is constructed between Newton iterations 3 and 4.} 
\end{figure}
